### 2018-08-07 paper/design.tex
section 3

\sonja{will frame and structure (A) squad overlay (prediction) (B)
  global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
  general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
  if not included earlier (F) out-of-band}
\commentDaniel{I suggest the following structure:
  (A) Sphinxes
  (B) SPOR (global overlay)
  (C) SPORES (local overlay).
  My original idea was to make Sphinxes its own section before the design 
  section instead of a subsection in the design section.}

@@

\begin{description}
\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. 
\item [Predictive.] The choice of nodes included in the onion routing
  layers is based on a predictive model for availability, disseminated
  according to Figure~\ref{fig:outline}, and queried by random peer sampling.
\item [Probabilistic.] Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way,
  resulting in a source-bounded random walk.
\item[Onion Routing.] Put simply, in onion routing, the sender creates
  a source route and 
  encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on
  Sphinx~\cite{Sphinx}, with some modification to allow for the
  changes above, described in \cref{Sphinxes}.
\end{description}

@@

We first describe \sphinxes (\cref{Sphinxes}), which is an adaptation of the

@@

Sphinx~\cite{Sphinx} mix-header format.
This means that we inherit some properties from Sphinx and due to being only a 
header format, it only imposes some restrictions in the above categories.
Sphinxes provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, Sphinxes is hybrid source-hop-by-hop routed, a
source-bounded random walk (communication 
model),
Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active \sonja{global?} adversary can learn the 
entire set).

Sphinxes does \emph{not} introduce any restrictions on whether the network 
topology must be fully connected or not, be asynchronous (as in Tor) or 
synchronous (as in mix-nets), whether node selection must be uniformly random 
or not.
Just as Sphinx, it can be used in many different settings.

Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
\commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
This focuses on the node selection, \ie adds node selection on top of Sphinxes.
The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

@@

\include*{sphinxes}
\include*{spor}
\commentAL{What I want to do from here:
(1) The squad overlay, where a user's devices exchange behavioral information;
(2) Predicting a device's availability;
(3) What is at the moment III-B SPOR: global overlay (one-liner: ``we use a RPS service'') and nodes selection per layer etc.;
(4) File exchange.}
\include*{squad-overlay-design}
\include*{file-transfer-design}

>>>>

\sonja{will frame and structure (A) squad overlay (prediction) (B)
  global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
  general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
  if not included earlier (F) out-of-band}
\commentDaniel{I suggest the following structure:
  (A) \Sphinxes
  (B) SPOR (global overlay)
  (C) SPORES (local overlay).
  My original idea was to make \Sphinxes its own section before the design 
  section instead of a subsection in the design section.}

@@

\begin{description}
\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. 
\item [Predictive.] The choice of nodes included in the onion routing
  layers is based on a predictive model for availability, disseminated
  according to Figure~\ref{fig:outline}, and queried by random peer sampling.
\item [Probabilistic.] Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way,
  resulting in a source-bounded random walk.
\item[Onion Routing.] Put simply, in onion routing, the sender creates
  a source route and 
  encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on
  Sphinx~\cite{Sphinx}, with some modification to allow for the
  changes above, described in \cref{\Sphinxes}.
\end{description}

@@

We first describe \sphinxes (\cref{\Sphinxes}), which is an adaptation of the

@@

Sphinx~\cite{Sphinx} mix-header format.
This means that we inherit some properties from Sphinx and due to being only a 
header format, it only imposes some restrictions in the above categories.
\Sphinxes provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, \Sphinxes is hybrid source-hop-by-hop routed, a
source-bounded random walk (communication 
model),
\Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active \sonja{global?} adversary can learn the 
entire set).

\Sphinxes does \emph{not} introduce any restrictions on whether the network 
topology must be fully connected or not, be asynchronous (as in Tor) or 
synchronous (as in mix-nets), whether node selection must be uniformly random 
or not.
Just as Sphinx, it can be used in many different settings.

Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
\commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
This focuses on the node selection, \ie adds node selection on top of \Sphinxes.
The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

@@

\include*{sphinxes}
\include*{spor}
\include*{squad-overlay-design}
%\include*{file-transfer-design}

### 2018-08-07 paper/spor.tex
section 3

\commentAL{I would like to merge that with \ref{ssec:por}.}

@@

There are many uses of Sphinxes, many criteria that can be used to select the 
nodes in each layer.
We will focus on maximizing availability when routing in a network with high 
churn, but one could equally well select nodes to maximize, \eg, bandwidth.
We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
from a source to a destination over a network of nodes with high churn.

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\avail_d(t)\) is the node's probability of being online as a function 
    of time.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}.
But even a solution like Tor's authoritative directory servers would work,
We will treat \(\avail_d\) in \cref{sec:squad_overlay}.

When Bob runs \(\CreateReply\) (or Alice runs \(\CreateFwd\)) he must supply a 
set of nodes for each layer of the route, \(L = \{L_0, \dotsc, L_\nu\}\), where 
\(|L_i| \leq w_L\) for \(0\leq i\leq \nu\).
The set \(L_\nu\) contains only one or more of Bob's devices.
For the other layers, \(L_i\) for \(i < \nu\), Bob will do the following:
Bob queries \(\GetRandomNode\) \((\nu-1)\cdot w_L\) times to get enough nodes 
to fill all remaining layers.
Bob will distribute these nodes across all layers \(L_i\) to maximize \(\min_i 
  \avail_{L_i}(t)\), where \(\avail_{L_i}(t) = 1-\prod_{l\in L_i} 
  (1-\avail_l(t))\).
This means that Bob minimizes the risk of a layer (\ie all nodes in a layer) 
being unavailable.

>>>>

@@

There are many uses of \Sphinxes, many criteria that can be used to select the 
nodes in each layer.
We will focus on maximizing availability when routing in a network with high 
churn, but one could equally well select nodes to maximize, \eg, bandwidth.
We now describe a protocol, \ac{SPOR}, which uses \Sphinxes to transfer messages 
from a source to a destination over a network of nodes with high churn.

\((d, \pk_d, \Pon_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \Pon_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\Pon_d(t)\) is the node's probability of being online as a function 
    of time.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}.
But even a solution like Tor's authoritative directory servers would work,
We will treat \(\Pon_d\) in \cref{sec:squad_overlay}.

When Bob runs \(\CreateReply\) (or Alice runs \(\CreateFwd\)) he must supply a 
set of nodes for each layer of the route, \(L = \{L_0, \dotsc, L_\nu\}\), where 
\(|L_i| \leq w_L\) for \(0\leq i\leq \nu\).
The set \(L_\nu\) contains only one or more of Bob's devices.
For the other layers, \(L_i\) for \(i < \nu\), Bob will do the following:
Bob queries \(\GetRandomNode\) \((\nu-1)\cdot w_L\) times to get enough nodes 
to fill all remaining layers.
Bob will distribute these nodes across all layers \(L_i\) to maximize \(\min_i 
  \Pon_{L_i}(t)\), where \(\Pon_{L_i}(t) = 1-\prod_{l\in L_i} 
  (1-\Pon_l(t))\).
This means that Bob minimizes the risk of a layer (\ie all nodes in a layer) 
being unavailable.

### 2018-08-07 paper/squad-overlay-design.tex
section 3

The exchanged data forms a sequence, ordered by timestamp, populated by three types of information:
\begin{itemize}
	\item \texttt{CONNECTED<$d, t_{step}$>}: Sent by device $d$ when it is used by its user at time step\footnote{As far as devices connections are concerned, time is discretized: we consider that each interaction lasts the same time.} $t_{step}$. $d$ is otherwise considered offline at this time. Devices use this information to predict their probability of remaining online, as presented in section~\ref{ssec:device_availability};
	\item \texttt{SENDING<\sendingdevice, \fileid>}: When the user decides to send a file $f$ located on a device \sendingdevice, \sendingdevice informs its peers of this fact, and joins the file ID \fileid. \Squad members will use this information to forward acknowledgments from the recipient to \sendingdevice;
	\item \texttt{RECEIVING<\recdevice, \fileid>}: Reciprocally, when the user starts receiving a file $f$ onto a device \recdevice, \recdevice informs its peers of this fact, and joins the file ID \fileid. \Squad members will use this information to forward the file's content from the sender to \recdevice.
\end{itemize}

Given this information dissemination and history reconciliation mechanism, each \squad member knows the full sequence $S$ at all times with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.

@@

The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\SPOR), as will be shown in the next subsection~\ref{ssec:por}.

@@

$P'd$ will be advertised in spite of $P_d$. It will also be used as a baseline in the evaluation.
\sonja{this and the next subsection seem redundant and need to be merged}
\subsection{Stateless Predictive Probabilistic Onion Routes}
\label{ssec:por}

\subsubsection{The global overlay}
\label{sssec:global_overlay}

Devices need to know the address of SPORES participants in order to craft PORs.
To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007} among all nodes in SPORES. \commentAL{TODO: cite \cite{Jesi_Montresor_van_Steen_2010} for \textbf{secure} RPS}.
It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the \emph{view} \rpsview). 
The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
Finally, offline nodes are quickly evicted from devices' views.

@@

In SPORES, a descriptor $\desc_d$ describing device $d$ contains the following information:
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(P_d\) is the node's probability of remaining online at the time of the descriptor's creation.
\end{itemize}

\subsubsection{Routes creation}
\label{sssec:routes_creation}

Routes are created via Sphinxes, as described in section~\ref{SPOR}.
Each layer \layer constituting the route is created by the same \CreateLayer\xspace function.

In \name, we wish to maximize the availability of the route.
Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
Note that Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.

\CreateLayer\xspace iteratively adds random descriptors from the RPS's view \rpsview to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:

$$ \Poff^\layer = \sum\limits_{d \in \layer}\desc_d.P_d $$

@@

Recall that each layer in Sphinxes has a constant number of nodes $w_\layer$, that is a Sphinxes parameter.
If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort \CreateLayer.
On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.

@@

In BitTorrent, .torrent files are publicly available on the Web.
They contain $\finfo = \left(\filesize, \nchunks, \left[\hashchunk\right]_{\text{chunk} \in f}, \hashfile\right)$, 
along with network information to reach uploaders of $f$ (e.g. the tracker's address).
Anyone can download a .torrent file and start receiving the file associated to it.

In \name, we want file exchanges to remain private: these metadata are exchanged out-of-band.
In addition, each file is associated with a random \fileid, that is part of \finfo.

\paragraph*{Out-of-band initialization} 
When Alice wishes to send a file $f$ to Bob, she computes \finfo, 
plus one reply header per chunk, and sends the whole to Bob.
Still out-of-band, Bob replies with one forward header per chunk.

@@

\paragraph*{Chunks and bitfields}
Alice's file $f$ is located on one of her devices, \sendingdevice. 
Each chunk $c_i \in f$ is uploaded to Bob through a unique route $\mathcal{H}_{c_i}$.
When $d_f$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded, with a period of

Bob receives $f$ on a device \recdevice, but a chunk $c_i$ for $f$ might arrive on any of his devices. 
This device then fetches the address of the proper recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its \squad sequence, 
and forwards the file chunk to \recdevice.
Upon reception of the chunk, \recdevice verifies its integrity by computing its SHA1 hash $h_{c_i}$ and comparing it to $\finfo.h_{c_i}$.
If the chunk is valid, \recdevice updates its \emph{bitfield} \bitfield: this bit-array of size \nchunks is initialized with 0;
every time Bob successfully receives a chunk $c_i$, \recdevice sets the bit $\bitfield[i]$.
To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{c_i}$.

Reciprocally, acknowledgments can arrive to Alice on any on her devices, while only \sendingdevice can process it.
When one of Alice's devices receives Bob's bitfield \bitfield, 
it forwards \bitfield to \sendingdevice by getting its address on the line \texttt{RECEIVING<\sendingdevice, \fileid>} of the \squad overlay's sequence.
Upon reception of a bitfield \bitfield, \recdevice updates its knowledge of Bob's unreceived chunks of $f$,
and sends a chunk to Bob among the ones that were not already acknowledged by Bob, unless the file has been entirely received.

>>>>

The exchanged messages form a sequence, ordered by timestamp, populated by three message types:
\begin{itemize}
	\item \texttt{CONNECTED<$d, t_{step}$>}: Sent by device $d$ when it is used by its user at time step\footnote{As far as devices connections are concerned, time is discretized: we consider that each interaction lasts the same time.} $t_{step}$. $d$ is otherwise considered offline at this time. Devices use this information to predict their probability of remaining online, as presented in section~\ref{ssec:device_availability};
	\item \texttt{SENDING<\sendingdevice, \fileid>}: When the user decides to send a file $f$ located on a device \sendingdevice, \sendingdevice informs its peers of this fact, and joins the file ID \fileid. Squad members will use this information to forward acknowledgments from the remote to \sendingdevice;
	\item \texttt{RECEIVING<\recdevice, \fileid>}: Reciprocally, when the user starts receiving a file $f$ onto a device \recdevice, \recdevice informs its peers of this fact, and joins the file ID \fileid. Squad members will use this information to forward the file's content from the remote to \recdevice.
\end{itemize}

Given this information dissemination (push) and history reconciliation mechanism (pull), each \squad member knows the full sequence $S$ at all time with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.

@@

The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
This information is used when any node needs to create a Probabilistic Onion Route (POR), as will be shown in the next subsection~\ref{ssec:por}.

@@

$P'd$ will be advertised in spite of $P_d$. It will also be used as a baseline in the evaluation.

%\subsection{Probabilistic Onion Routes}
\subsection{Selection of nodes for routes creation}
\label{ssec:por}

%\subsubsection{The global overlay}
\subsubsection{\GetRandomNode}
\label{sssec:global_overlay}

Devices need to know the address of SPORES participants in order to craft PORs.
To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007,Jesi_Montresor_van_Steen_2010} (RPS) among all nodes in SPORES.
It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the RPS's \emph{view} \rpsview). 
The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
Finally, offline nodes are quickly evicted from devices' views.

@@

In SPORES, a descriptor $\desc_d$ describing device $d$ contains the following information:
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\Pon_d\) is the node's probability of remaining online at the time of the descriptor's creation.
\end{itemize}

$(d, \pk_d, \Pon_d)= \leftarrow \GetRandomNode$ is the function that takes a node from the RPS's view \rpsview on demand.

%\subsubsection{Routes creation}
\subsubsection{\CreateLayer}
\label{sssec:routes_creation}

Routes are created via \Sphinxes as described in section~\ref{sec:SPOR}.
But each layer \layer constituting the route is created by the $\CreateLayer$ function, that is independent from \Sphinxes.

In \name, we wish to maximize the availability of the route.
Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
Note that \Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.

$\CreateLayer$ iteratively calls $\GetRandomNode\xspace$ to add random nodes to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:

$$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$

@@

Recall that each layer in \Sphinxes has a constant number of nodes $w_\layer$, that is a \Sphinxes parameter.
If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort $\CreateLayer$.
On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.

@@

In BitTorrent, .torrent files are publicly available on the Web.
They contain $\finfo = \left(\filesize, \nchunks, \left[\hashchunk\right]_{\chunk \in f}, \hashfile\right)$, 
along with network information to reach uploaders of $f$ (e.g. the tracker's address).
Anyone can download a .torrent and start receiving the file associated to it.

In \name, we want file exchanges to remain private: the file's metadata are exchanged out-of-band.
In addition , each file is associated with a random \fileid, that is part of \finfo.

\newcommand\forwardheader{\ensuremath{\mathcal{H}^{(f)}}}
\newcommand\backwardheader{\ensuremath{\mathcal{H}^{(b)}}}

\paragraph*{Out-of-band initialization} 
When Alice wishes to send a file $f$ to Bob, she computes \finfo, 
plus one reply header per chunk (as was seen in section~\ref{sec:SPOR}), and sends the whole to Bob.
Still out-of-band, Bob replies with one forward header per chunk.
This way, each chunk $\chunk_i$ is associated with a unique route both ways: 
a forward header $\forwardheader_i$ known by Alice, and a backward header $\backwardheader_i$ known by Bob.

@@

\paragraph*{Chunks and bitfields}
Alice's file $f$ is located on one of her devices, \sendingdevice. 
When $\sendingdevice$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded, with a period of \tupload.
Each chunk $\chunk_i \in f$ is uploaded to Bob through a unique route $\forwardheader_i$.

Bob receives $f$ on a single device \recdevice, but chunks for $f$ might arrive on any of his devices.
Say Bob has received a chunk $\chunk_i$ on $d \neq \recdevice$.
This device must the address of the file's recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its squad sequence.
Having found the address of \recdevice, $d$ forwards the $\chunk_i$ to \recdevice.

Upon reception of a chunk $\chunk_i$, \recdevice verifies its integrity by computing the SHA1 hash $h_{\chunk_i}$ and comparing it to $\finfo.h_{\chunk_i}$.
If the chunk is valid, Bob must inform Alice that $\chunk_i$ was successfully received.
We borrow again from the BitTorrent protocol by acknowledging reception with \emph{bitfields}.
A bitfield \bitfield is bit-array of size \nchunks, such that $\bitfield[i] = 0$ means that Bob lacks the chunk $\chunk_i$, whereas $\bitfield[i] = 1$ means that he successfully received that chunk.
$\bitfield$ describes the state of the total transfer and not just the current chunk, which is very useful when messages are prone to get lost in transit. 
This bitfield is sent to Alice using the unique reply route $\backwardheader_i$.

% Every time Bob successfully receives a chunk $\chunk_i$, \recdevice sets the bit $\bitfield[i]$, 
% To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{\chunk_i}$.

Reciprocally, acknowledgments can arrive to Alice on any on her devices, while only \sendingdevice can process it.
When one of Alice's devices (say $d'$) receives Bob's bitfield \bitfield, 
$d'$ forwards it to \sendingdevice by getting its address on the line \texttt{RECEIVING<\sendingdevice, \fileid>} of the \squad overlay's sequence.

Once \sendingdevice receives \bitfield, it merges it with its previous knowledge of Bob's reception of $f$.
If all chunks were acknowledged, the transfer is over.
Else, \sendingdevice sends a new chunk, among the ones that were not acknowledged by Bob.
